Convergent Evolution During Local Adaptation to Patchy Landscapes

### 2015-09-08 patchy-review-responses-second-round.tex

%%%%%%
\point{}{
I still think that the main result (11) is dimensionally inconsistent -- it needs to be integrated over the boundary layer of the patch. In their response to my original review, the authors just referred to their response to a similar point by reviewer 1, but I don't think that this addresses my concern -- reviewer 1 was talking about integrating over a different area, the one occupied by a family, which I agree is not correct. (Note that the 1D simulations aren't going to be able to catch this issue, since you can't play with the length of the boundary.)
}

\reply
As discussed above, we fixed this.
And, apologies for not catching on in the first round of reviews.

%%%%%%
\point{}{
I do think that reviewer 1 raises a good point though. Looking back through the manuscript, I can't find where the authors show that the family is localized within a length scale $\sim \sigma/\sqrt{s_m} \ll A^{1/d}$. This is important, since it's needed to justify the approximation that the whole family arrives at the patch together. This seems like a basic fact about subcritical branching random walks/Brownian motions, so there's probably a formal proof of it somewhere in the literature, but I think that it's straightforward to give an intuitive explanation.
}

\reply
Good point; we've added this, and it works out nicely: \revref.
We have looked a fair bit for a formal proof in the literature and not turned it up.
There are general results that say that for small $s$, 
a subcritical branching process looks nearly like the critical case,
where for instance $\P\{Z_n s/(1-(1-s)^{-n}) \le u \given Z_n>0\} \simeq 1-e^{-2u/\var[Z_1]}$
\citep{jagers1975branching},
but it doesn't seem like invoking these results would simplify the exposition.

### 2015-09-11 patchy-selection-paper.tex
moved notes on lineage movement to clinal-lineages

\begin{figure}[ht!]
  \begin{center}
    \includegraphics{sim-occupation-freqs}
  \end{center}
  \caption{
  \textbf{(A)} 
  Mean occupation frequencies of individual demes (grey dots)
  and averaged over demes at similar distances (black circles) from simulations, 
  on a one-dimensional grid of 201 demes, and
  a two-dimensional grid of $101\times 101$ demes.
  Superimposed in color is the decay predicted by \eqref{eqn:eqfreq},
  with $C$ chosen arbitrarily to give a reasonable fit: 0.85 and 0.11 respectively.
  (The disagreement at long distances is due to boundary effects near the edge of the range.)
  \textbf{(B)} 
  Fluctuations: colored lines are snapshots of allele frequencies at evenly spaced times
  from a one-dimensional grid of 151 demes;
  the solid line shows the cumulative mean occupation frequency across all generations.
  For both plots, the simulation was run for 1000 generations;
  the focal allele is beneficial in the central 10 demes, with $s_p=0.1$,
  and deleterious elsewhere, with $s_m=-0.02$; 
  demes had 1000 individuals in each;
  dispersal was to nearby demes with mean dispersal distances of 
  $\sigma = 0.95$ and 0.74 times the deme spacing, respectively.
  More details are given below in \secref{ss:simulations}.
   }   \label{fig:sim_occupation_freqs}
\end{figure}

@@

\section*{Acknowledgements}
We would like to heartily thank Joachim Hermisson, Richard Neher, and an anonymous reviewer
for a number of insightful suggestions,
and catching several errors present in earlier drafts. \revpoint{3}{4}
We would also like to acknowledge Michael Nachman, Steve Evans, and Yaniv Brandvain for useful discussions, 
as well as Gideon Bradburd, and Simon Aeschbacher and the rest of the Coop lab
for helpful comments and discussion of the manuscript.
This work was supported by grants from the
National Science Foundation under Grant No.\ 1262645 to PLR and GC and by the
National Institute of General Medical Sciences of the National
Institutes of Health under award numbers NIH RO1GM83098 and
RO1GM107374 to GC.

@@

% endfloat uses different names
\ifsubmissionversion
  \renewcommand{\thesfigure}{S\arabic{sfigure}}
  \renewcommand{\thepostsfigure}{S\arabic{postsfigure}}
  % \renewcommand{\thefigure}{S\arabic{figure}}
  % \renewcommand{\thepostfigure}{S\arabic{postfig}}
  % \setcounter{postfig}{0}
  \renewcommand{\thetable}{S\arabic{table}}
  \renewcommand{\theposttable}{S\arabic{posttable}}
  \setcounter{posttable}{0}
\fi

>>>>

\begin{figure}[ht!]
  \begin{center}
    % made in patchy-sim-writeup-plots.R
    \includegraphics{sim-occupation-freqs}
  \end{center}
  \caption{
  \textbf{(A)} 
  Mean occupation frequencies of individual demes (grey dots)
  and averaged over demes at similar distances (black circles) from simulations, 
  on a one-dimensional grid of 201 demes, and
  a two-dimensional grid of $101\times 101$ demes.
  Superimposed in color is the decay predicted by \eqref{eqn:eqfreq},
  with $C$ chosen arbitrarily to give a reasonable fit: 0.85 and 0.11 respectively.
  (The disagreement at long distances is due to boundary effects near the edge of the range.)
  \textbf{(B)} 
  Fluctuations: colored lines are snapshots of allele frequencies at evenly spaced times
  from a one-dimensional grid of 151 demes;
  the solid line shows the cumulative mean occupation frequency across all generations.
  For both plots, the simulation was run for 1000 generations;
  the focal allele is beneficial in the central 10 demes, with $s_p=0.1$,
  and deleterious elsewhere, with $s_m=-0.02$; 
  demes had 1000 individuals in each;
  dispersal was to nearby demes with mean dispersal distances of 
  $\sigma = 0.95$ and 0.74 times the deme spacing, respectively.
  More details are given below in \secref{ss:simulations}.
   }   \label{fig:sim_occupation_freqs}
\end{figure}

@@

\section*{Acknowledgements}
We would like to heartily thank Joachim Hermisson, Richard Neher, and an anonymous reviewer
for a number of insightful suggestions,
and catching several errors present in earlier drafts. \revpoint{3}{4}
We would also like to acknowledge Michael Nachman, Steve Evans, and Yaniv Brandvain for useful discussions, 
as well as Gideon Bradburd, and Simon Aeschbacher and the rest of the Coop lab
for helpful comments and discussion of the manuscript.
\ifsubmissionversion
% PLoS puts this somewhere else
\else
This work was supported by grants from the
National Science Foundation under Grant No.\ 1262645 to PLR and GC and by the
National Institute of General Medical Sciences of the National
Institutes of Health under award numbers NIH RO1GM83098 and
RO1GM107374 to GC.
\fi

@@

% endfloat uses different names
\renewcommand{\thesfigure}{S\arabic{sfigure}}
\renewcommand{\thetable}{S\arabic{table}}
\ifsubmissionversion
  \renewcommand{\thepostsfigure}{S\arabic{postsfigure}}
  % \renewcommand{\thefigure}{S\arabic{figure}}
  % \renewcommand{\thepostfigure}{S\arabic{postfig}}
  % \setcounter{postfig}{0}
  \renewcommand{\theposttable}{S\arabic{posttable}}
  \setcounter{posttable}{0}
\fi
